---
title: "Models Available in DSL"
output: 
  md_document:
    variant: markdown_github
---

<div class="card bg-light mb-3">
<div class="card-header">**Table of Contents**</div>
<div class="card-body">

- [**`lm`: Linear Regression**](#lm) <br>

- [**`logit`: Logisitc Regression**](#logit) <br>

- [**`felm`: Fixed Effects Linear Regression**](#felm) <br>


</div>
</div>

Note: We currently cover three models (`lm`, `logit`, `felm`). In the next update, we are planning to add more models, including multinomial-logit regression, poisson regression, and two-stage least squares for the instrumental variable method. 

<br>

### **`lm`: Linear Regression**{#lm} 
<p class="lh-lg">
</p>

Researchers can implement DSL linear regression by specifying `model = "lm"`. 

```{r eval = TRUE, echo = TRUE, tidy = FALSE, warning = FALSE, error = FALSE, message = FALSE}
library(dsl)
data("data_lm") # example data 
head(data_lm)
```

In this example, variable `Y` requires text annotation (they take `NA` if a given observation is not labeled by experts). Variable `pred_Y` represents predictions for `Y`.

```{r eval = TRUE, echo = TRUE, tidy = FALSE, warning = FALSE, error = FALSE, message = FALSE}
out_lm <- dsl(model = "lm", 
              formula = Y ~ X1 + X2 + X3 + X4 + X5,
              predicted_var = "Y",
              prediction = "pred_Y",
              data = data_lm)
```

| Argument | Description              |
|:-------- | :------------------------|
|`model` | A regression model. `dsl` currently supports `lm` (linear regression), `logit` (logistic regression), and `felm` (fixed-effects regression).|
|`formula` | A formula used in the specified regression model.|
|`predicted_var` | A vector of column names in the data that correspond to variables that need to be predicted.|
|`prediction` | A vector of column names in the data that correspond to predictions of `predicted_var`. |
| `data`    | A data frame. The class should be `data.frame`.|

```{r eval = TRUE, echo = TRUE, tidy = FALSE, warning = FALSE, error = FALSE, message = FALSE}
summary(out_lm)
```

<br>

### **`logit`: Logistic Regression**{#logit} 
<p class="lh-lg">
</p>

Researchers can implement DSL logistic regression by specifying `model = "logit"`. It requires the same arguments as `model = "lm"`. 

```{r eval = TRUE, echo = TRUE, tidy = FALSE, warning = FALSE, error = FALSE, message = FALSE}
data("data_logit") # example data 
head(data_logit)
```

In this example, variables `Y` and `X1` require text annotation (they take `NA` if a given observation is not labeled by experts). Variables `pred_Y` and `pred_X1` represent predictions for `Y` and `X1`. As in this example, `dsl` can handle cases when multiple variables require text annotations.

```{r eval = TRUE, echo = TRUE, tidy = FALSE, warning = FALSE, error = FALSE, message = FALSE}
out_logit <- dsl(model = "logit", 
                 formula = Y ~ X1 + X2 + X4,
                 predicted_var = c("Y", "X1"),
                 prediction = c("pred_Y", "pred_X1"),
                 data = data_logit)
summary(out_logit)
```

<br>

### **`felm`: Fixed Effects Linear Regression**{#felm} 
<p class="lh-lg">
</p>

Researchers can implement DSL fixed effects linear regression by specifying `model = "felm"`. 

```{r eval = TRUE, echo = TRUE, tidy = FALSE, warning = FALSE, error = FALSE, message = FALSE}
data("data_lm")  # example data 
head(data_felm)
```

In this example, variable `log_gsp` requires text annotation (it takes `NA` if a given observation is not labeled by experts). Variable `pred_log_gsp` represents predictions for `log_gsp`. 


#### One-way Fixed Effects

To implement DSL one-way fixed effects regression, users can set `fixed_effect = "oneway"`. Use `index` to denote which column defines fixed effects. Users can also cluster standard errors by specifying a variable name in argument `cluster` (this `cluster` argument is also avaiable for other models). 

```{r eval = TRUE, echo = TRUE, tidy = FALSE, warning = FALSE, error = FALSE, message = FALSE}
out_felm_one <- dsl(model = "felm", 
                    formula = log_pcap ~ log_gsp + log_pc + unemp,
                    predicted_var =  "log_gsp",
                    prediction = "pred_log_gsp",
                    fixed_effect = "oneway", 
                    index = c("state"), 
                    cluster = "state",
                    data = data_felm)
```
| Argument | Description              |
|:-------- | :------------------------|
|`fixed_effect` | A type of fixed effects regression you run. `oneway` (one-way fixed effects) or `twoways` (two-way fixed effects).|
|`index` | A vector of column names specifying fixed effects. When `fixed_effect = oneway`, it has one element. When `fixed_effect = twoways`, it has two elements, e.g., `index = c("state", "year")`. |
|`cluster` | A column name in the data that indicates the level at which cluster standard errors are calculated. Default is `NULL`.|


```{r eval = TRUE, echo = TRUE, tidy = FALSE, warning = FALSE, error = FALSE, message = FALSE}
summary(out_felm_one)
```

#### Two-way Fixed Effects

To implement DSL two-way fixed effects regression, users can set `fixed_effect = "twoways"`. Use `index` (a vector of length 2) to denote which columns define fixed effects. 

```{r eval = TRUE, echo = TRUE, tidy = FALSE, warning = FALSE, error = FALSE, message = FALSE}
out_felm_two <- dsl(model = "felm", 
                    formula = log_pcap ~ log_gsp + log_pc + unemp,
                    predicted_var =  "log_gsp",
                    prediction = "pred_log_gsp",
                    fixed_effect = "twoways", 
                    index = c("state", "year"), 
                    cluster = "state",
                    data = data_felm)
```

```{r eval = TRUE, echo = TRUE, tidy = FALSE, warning = FALSE, error = FALSE, message = FALSE}
summary(out_felm_two)
```
